I don't know, are you sure you want to do this?

### 2016-10-07 submission/paper.tex
Bib file for references

\subsection{Local sea level}
In order to get from global sea level projections to local ones, it is important to note that sea level rise not is uniform over the globe. Glacial and land ice melting affect the local sea level differently depending on where the melted ice is located.
%Gravitaional effects
Another major effect in Fennoskandia is the land rise due to isostatic effects of the glaciers from the last ice age.
Again, we will use historical data to relate global sea level to isostatically corrected local sea level using a time series regression model. 
%Figure showing corrected and uncorrected Bergen data and regression model.

@@

%%  REFERENCE LIST AND TEXT CITATIONS
% 5\bibliographystyle{../BibTeX/agufull08}
\bibliographystyle{agufull08}
% \bibliography{ref.bib}
% Please use ONLY \citet and \citep for reference citations.

\begin{thebibliography}{37}
%%   Before submitting: copy all the contents into the .bbl LaTeX file here
%%   and run latex again
\providecommand{\natexlab}[1]{#1}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
  \providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
  \urlstyle{rm}\Url}\fi

\bibitem[{Bolin et~al.(2014)}]{Bolin2014a}
Bolin, D., P. Guttorp, A. Januzzi, M. Novak, H. Podschwit, L. Richardson, C. Sowder, A. S\"{a}rkk\"{a} and A. Zimmerman (2014), Statistical prediction of global sea level from
  global temperature. \textit{Statistica Sinica},~{\em25}, 351--367.

\bibitem[{Church and White (2011)}]{csiro}
Church, J. and N.~White (2011),
Sea-level rise from the late 19th to the early 21st century.
{\em Surveys in Geophysics\/}~{\em 32}, 585--602.

\bibitem[{\textit{Fankhauser et~al.}(1999)}]{Fankhauser&1999}
  Fankhauser, S., J.~B.~Smith, and R.~S.~J.~Tol (1999), {Weathering climate
    change: some simple rules to guide adaptation decisions},
  \textit{Ecological Economics}, \textit{30}, 67--78.

 \bibitem[{Guttorp et~al. (2014)}]{Guttorp2014}
Guttorp, P., D. Bolin, A. Januzzi, D. Jones, M. Novak, H. Podschwit, L. Richardson, A.
S\"{a}rkk\"{a}, C. Sowder and A Zimmerman (2014), Assessing the uncertainty in projecting local
mean sea level from global temperature. \textit{Journal of Applied Meteorology and Climatology}.
\textit{53}, 2163--2170.

  \bibitem[{Hansen et~al.} (2001)]{giss}
Hansen, J., R.~Rued, M.~Sato, M.~Imhoff, W.~Lawrence, D.~Easterling,
  T.~Peterson, and T.~Karl (2001),
A closer look at {U}nited {S}tates and global surface temperature
  change. {\em J. Geophys. Res.\/}~{\em 106}, 23947--23963.

 \bibitem[{Rahmstorf}{2007}]{Rahmstorf07}
Rahmstorf, S. (2007).
\newblock {A} semi-empirical approach to projecting future sea-level rise.
\newblock {\em Science\/}~{\em 315}, 368--370.

\bibitem[{Rahmstorf, Perrette, and Vermeer}{Rahmstorf
  et~al.}{2011}]{Rahmstorf11}
Rahmstorf, S., M.~Perrette, and M.~Vermeer (2011),
Testing the robustness of semi-empirical sea level projections.
  climate dynamics.
{\em Climate Dynamics}~{\em 39}, 861--875.

\bibitem[{Robert and Casella}(2004)]{RobertCasella2004}
Robert, C.~P., and G.~Casella (2004), \textit{Monte Carlo Statistical Methods},
  2nd ed., Springer, New York.

\bibitem[{Rue et~al.}(2009)]{Rueetal2009}
Rue, H., S.~Martino, and N.~Chopin (2009), {Approximate {B}ayesian Inference
  for Latent {G}aussian Models Using Integrated Nested {L}aplace Approximations
  (with Discussion)}, \textit{Journal of the Royal Statistical Society, Series
  B}, \textit{71}, 319--392.

\bibitem[{Taylor et~al.(2012)Taylor, Stouffer, and Meehl}]{cmip5}
Taylor, K., R.~Stouffer, and G.~Meehl, 2012: An overview of {CMIP}5 and the
  experiment design. \textit{Bull. Amer. Meteor. Soc.}, \textbf{93}, 485--498.

\end{thebibliography}

>>>>

\subsection{Local sea level}
In order to get from global sea level projections to local ones, it is important to note that sea level rise not is uniform over the globe. Glacial and land ice melting affect the local sea level differently depending on where the melted ice is located.
%Gravitaional effects
Another major effect in Fennoskandia is the land rise due to isostatic rebound from the glaciers of the last ice age. 
Again, we will use historical data to relate global sea level to isostatically corrected local sea level using a time series regression model. 
%Figure showing corrected and uncorrected Bergen data and regression model.

@@

%%  REFERENCE LIST AND TEXT CITATIONS
% 5\bibliographystyle{../BibTeX/agufull08}
\bibliographystyle{agufull08}
\bibliography{ref.bib}
% Please use ONLY \citet and \citep for reference citations.

%\begin{thebibliography}{37}
%%   Before submitting: copy all the contents into the .bbl LaTeX file here
%%   and run latex again
%\providecommand{\natexlab}[1]{#1}
%\expandafter\ifx\csname urlstyle\endcsname\relax
%  \providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
%  \providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
%  \urlstyle{rm}\Url}\fi

%\end{thebibliography}
